The GitHub Open Source Development Process \author{Kevin Peterson\\ \small \texttt{kevin@kevinp.me} }

### 2014-08-14 paper/main.tex
Fixed a typo.
Removed some contact info from the header of main, as well as the interviews.

\title{
The GitHub Open Source Development Process
\author{Kevin Peterson\\
Department of Information Technology\\
Clinical Informatics Support Systems\\
Mayo Clinic\\
200 1st Street\\
Rochester, MN  55905\\
\small \texttt{peterson.kevin@mayo.edu}
}
}

@@

Figure~\ref{fig:issue_reporters_committers_scatterplot}, does however suggest, however, that that the two variables are related. The hypothesis implies that there will be a correlation between the two variables -- which is demonstrated by a reasonably strong correlation coefficient of \input{issue_reporters_committers_scatterplot-correlation}}\unskip. More investigation would be necessary to further examine this finding.\\

@@

\input{interview}
\input{github_interview}

>>>>

\title{
The GitHub Open Source Development Process
\author{Kevin Peterson\\
\small \texttt{kevin@kevinp.me}
}
}

@@

Figure~\ref{fig:issue_reporters_committers_scatterplot} does suggest, however, that that the two variables are related. The hypothesis implies that there will be a correlation between the two variables -- which is demonstrated by a reasonably strong correlation coefficient of \input{issue_reporters_committers_scatterplot-correlation}}\unskip. More investigation would be necessary to further examine this finding.\\

@@

%\input{interview}
%\input{github_interview}
